Transient Variability In Vapor Intrusion And The Factors That Influence It

### 2019-03-04 tex/main.tex
Added structure notes
Writing

@@

\begin{figure}[!h]
		\centering
    \caption{ }
    \label{fig:pair_grid}
    \includegraphics[width=\textwidth]{simple_grid.pdf}
\end{figure}

>>>>

\begin{equation}
  V \frac{\partial c_\mathrm{in}}{\partial t} = n - c_\mathrm{in} A_e V \label{eq:indoor_air}
\end{equation}

@@

\begin{figure}[!h]
		\centering
    \caption{Distributions of indoor/outdoor pressure differences (top row), and its correlation with indoor air contaminant concentrations (middle rows), and air exchange rate (bottom row), at three different VI sites - ASU house, Indianapolis site, and North Island NAS.}
    \label{fig:pair_grid}
    \includegraphics[width=\textwidth]{simple_grid.pdf}
\end{figure}

Our discussion of examining the temporal variability of indoor air contaminant concentration begins by considering one of the most dynamic factors that influence VI - the indoor/outdoor pressure difference ($p_\mathrm{in/out}$).
In the top row of Figure \ref{fig:pair_grid}, the distribution of $p_\mathrm{in/out}$ at three difference VI sites, the ASU house, Indianapolis site, and North Island NAS, are plotted.
The distributions of $p_\mathrm{in/out}$ at these three site resemble normal-like distribution, with a mean of a few negativa Pa, indicating that the most probable state is that these sites are slightly depressized.
At the ASU house and the Indianapolis site, the range of $p_\mathrm{in/out}$ values are relatively similar, whereas the North Island NAS site has significalty larger span of values.
This is most likely due to the poor structural condition of the North Island site, making it much more suspectible to barometric pressure fluctations; the ASU house and Indianapolis site regular residential structure in good condition.
The periods when the preferential pathway at the ASU house was open and closed are considered separately.
% TODO: Add some sort of interesting conclusion

Now we move on to look at $p_\mathrm{in/out}$ is correlated with the indoor air contaminant concentration ($c_\mathrm{in}$).
The middle row of Figure \ref{fig:pair_grid} shows the log-10 values of $c_\mathrm{in}$ vs. $p_\mathrm{in/out}$, placed into evenly spaced bins, are plotted.
Each bin represents the mean $c_\mathrm{in}$ and the errorbars show the 95\% confidence interval. % TODO: Change this description once you've fixed the figure.
A linear regression curve is also fitted to the data, with the shaded part of the regression again indicating the 95\% confidence interval. % TODO: Make sure this is right.
At the ASU house, it is readibly apparent that the preferential pathway has a profound effect on how sensitive $c_\mathrm{in}$ is to $p_\mathrm{in/out}$, showing that the closing of the preferential pathway fundamentally changes the site.
Perhaps surprsingly, when the preferential pathway is closed $p_\mathrm{in/out}$ is not strongly correlated with $c_\mathrm{in}$.

It is clear that $p_\mathrm{in/out}$ sets a trend, i.e. increased depressurziation is associated with higher $c_\mathrm{in}$, but there is still considerable variability for a given $p_\mathrm{in/out}$.

$p_\mathrm{in/out}$ is important in determining the contaminant entry rate into a structure, but it also will partly determine the air exchange rate.
How significantly $p_\mathrm{in/out}$ determines $A_e$ varies significantly with site specific conditions, e.g. HVAC operation, if windows are open/closed, how well insulted the structure is etc.
$A_e$ is thus highly variate for a given $p_\mathrm{in/out}$ hypothesize that most of this variability may be explained by variation in air exchange rate ($A_e$).

Air exchange

This leads us to examine how $A_e$ is associated with

The difference in correlation of $c_\mathrm{in}$ vs. $p_\mathrm{in/out}$ for the "open" and "closed" periods, as well as the $p_\mathrm{in/out}$ is more evenly distributed around 0 Pa support with our choice of model, where we assume that the preferential pathway acts by enhancing the "advective potential" of a VI site through improving communication between the indoor and outdoor.

% ASU:
% Pressure distributions similar
% Yet drastically different c
% => clearly driven by PP
% Pressure relationship better when open than close
% => Enhanced advection, motivating our choice of model
% Poor relationship for closed,
% => Diffusion dominated transport
% Yet significant uncertainty and variance in indoor air?
% Look at the influence of Ae on this
% Pressure is related to Ae, but not determinant
% => still large variability in Ae for a given p, what effect does this have?

% Indianapolis & North Island
% Unforunately no Ae data here like ASU, cannot look at that influence
% Stronger correlation between p and c here
% Indianapolis had some type of PP, though less significant than at ASU
% North Island had very large pressure changes, may explain the stronger relationship

% Constant Ae simulations
% First consider only pressure influence (constant Ae)
% PP Open
% Clearly we can capture the trend when p < 0, but not well when p > 0
% When p > 0, diffusion limit, but still variability, why?
% => Indicate fluctuating Ae
% Uniform soil
% Removing gravel sub-base removes the "upswing"
% Permeable subbase region necessary to realize "advective potential"
% PP closed
% Kind of capture a "trend", but not variability
% Pressure not significant and/or advective transport too inhibited to be signifncant
% => Indicate fluctating Ae driver for variability here
% Main point:
% Pressure controls Ae and entry rate, but in closed and uniform cases, it is insufficnet to dramatically increase entry rate
% When open, this is no longer true
% Pressure also help control Ae, but there is great uncertainty
% This leads to the difficult to predict variability
% => Need to incorporate Ae fluctuations to understand variability

% New PP simulations with extreme Ae values for each pressure considered
% Now we capture most of the variability for open and closed
% Strong indicator that fluctating Ae is responsible for a significant portion of the variability
% Needs to be controlled better (hard)
% Or the span of values considered to give upper and lower limits on variability
% Use EPA handbook to estimate variability (pretty much can always be one OOM)

% This says nothing about at what speed or timescale change may occur
% We look at the difference between max/min across various timespans
% See that on daily to a week, absent a PP, little variability is expected
% => 24 hr average samples adequate
% => no need to sample more than a few days apart
% Across time, more of the extreme values of Ae and pressure have occured, kind of ergodically, giving rise to this increase in variability
% Remember p and Ae are more or less normally distributed, (Ae more skewed)
% => extreme values unlikely but do happen across time

% Problem with attenuation to subslab
% Spatial variability in subslab may be greater than temporal indoor variability
% ASU perfect example, here there is greater alpha_sb variability than c
% => May be more uncertain
% => False positive for indoor sources
% => But could also indicate presence of PP in subbase
% Much larger spatial variability in subbase with PP present than without
% (Show plot with 2-4 panes)
% 1./2. show ASU/Indianapolis alpha_sb
% 3./4. model alpha_sb distributions with and without PP
